\ProjectName{}: Data Imputation as a Query Optimization

### 2016-12-14 paper/conclusion.tex
paper: add imputation cost/loss to further work

\subsection{Future Work}
\ProjectName{} opens up multiple avenues for further work. For instance, we could extend our minimal/maximal imputation
operators to consider global information, such as the specific columns needed in operators higher up in the query plan.
Our optimizer uses the same machine learning algorithm in all instances of imputation operators. Integrating multiple
possible algorithms could allow for further fine-grained imputation. Finally, the underlying database for \ProjectName{}
is far from a full-featured, production database, so a natural step is to integrate imputation planning in a widely-adopted
production-quality database. This will likely expose further opportunities for improvement.

>>>>

\subsection{Future Work}
\ProjectName{} opens up multiple avenues for further work. For instance, we
could extend our minimal/maximal imputation operators to consider global
information, such as the specific columns needed in operators higher up in the
query plan.  Our optimizer uses the same machine learning algorithm in all
instances of imputation operators. Integrating multiple possible algorithms
could allow for further fine-grained imputation, and honing the time complexity and
loss of these algorithms for an iterator model database could facilitate more
intelligent query plans and consistent interpretations of $\alpha$ across
strategies. For example, algorithms that learn in an online manner could
increase the efficiency of the system.  Furthermore, a multiple imputation
strategy could be followed for queries involving certain aggregates. Finally,
the underlying database for \ProjectName{} is far from a full-featured,
production database, so a natural step is to integrate imputation planning in a
widely-adopted production-quality database. This will likely expose further
opportunities for improvement.
